Automating Verification of MPC Security

### 2023-06-07 popl24/minicat.tex
checkpoint

\subsection{Syntax} The syntax of $\minifed$, defined in
Figure \ref{fig-minifed-syntax}, includes a standard boolean algebra
with $\eand$, $\eor$, $\exor$, and $\enot$ as primitives. In addition
programs have different kinds of variables, including \emph{secrets}
$\secret{\cid}{w}$, \emph{flips} $\flip{\cid}{w}$, and \emph{views}
$\view{\cid}{w}$.  Each of these variables are indexed by an ``owner''
client $\cid$ and distinguishing string $w$. So for example,
$\secret{\ttt{1}}{\ttt{foo}}$ is client $\ttt{1}$'s secret called
$\ttt{foo}$. All clients can make reference to the \emph{oracle}
through variables $\oracle{w}$- this is a form of shared randomness
that is standard in the MPC setting \cite{XXX}.  Each client can only
compute on their own variables in \emph{expressions} $\be$, and share
values with other clients by assignment to their views as in
$\eassign{\view{\cid}{w}}{\be}$.  A \emph{protocol} $\prog$ is a
possibly empty sequence of view assignments. We will generally omit
$\varnothing$ from example code, i.e., writing $c_1;\ldots;\c_n$
instead of $c_1;\ldots;\c_n;\varnothing$, and abusing notation we will
write $\prog_1;\prog_2$ to denote the concatenation of $\prog_1$
and $\prog_2$.

>>>>

\subsection{Syntax} The syntax of $\minifed$, defined in
Figure \ref{fig-minifed-syntax}, includes a standard boolean algebra
with $\eand$, $\eor$, $\exor$, and $\enot$ as primitives. In addition
programs have different kinds of variables, including \emph{secrets}
$\secret{\cid}{w}$, \emph{flips} $\flip{\cid}{w}$, and \emph{views}
$\view{\cid}{w}$.  Each of these variables are indexed by an ``owner''
client $\cid$ and distinguishing string $w$. So for example,
$\secret{\ttt{1}}{\ttt{foo}}$ is client $\ttt{1}$'s secret called
$\ttt{foo}$. All clients can make reference to the \emph{oracle}
through variables $\oracle{w}$- this is a form of shared randomness
that is standard in the MPC setting \cite{XXX}.  Each client can only
compute on their own variables in \emph{expressions} $\be$, and share
values with other clients by assignment to their views as in
$\eassign{\view{\cid}{w}}{\be}$.  A \emph{protocol} $\prog$ is a
possibly empty sequence of view assignments. We will generally omit
$\varnothing$ from example code, writing $\instr_1;\ldots;\instr_n$
instead of $\instr_1;\ldots;\instr_n;\varnothing$, and abusing notation we will
write $\prog_1;\prog_2$ to denote the concatenation of $\prog_1$
and $\prog_2$.

### 2023-06-07 popl24/pmf.tex
checkpoint

We consider random tapes to be selected from a uniform distribution.
In our threat model we will also assume that any possible initial
secrets are equally likely when formulating the program distribution.
In this setting, given a program $\prog$ with $\iov(\prog) = S \cup
V$ we will consider all $\store
\in \mems(\iov(\prog) \cup \flips(\prog))$ such that
$
\config{\store_{S \cup \flips(\prog)}}{\prog} \redxs \config{\store_}{\varnothing}
$
to be equally probable, establishing the basic distribution of the
program. From this we can immediately derive the marginal distribution
of $S \cup V$ to reason about dependencies between secrets and views. 
\begin{definition}
  \label{def-progd}
  Given progam $\prog$ with $\iov(\prog) = (S,V)$ and $\flips(\prog) = F$, define $\stores$ as:
  $$
  \stores \defeq \{ \store \mid (\dom(\store) = S \cup V \cup F) \wedge (\store_{S \cup F},\prog) \redxs (\store,\varnothing) \}
  $$
  Define also $\pdf{S \cup V \cup F}$ as the program's \emph{basic distribution} such that for all
  $\store \in \mems(S \cup V \cup F)$:
  $$
  \pdf{S \cup V \cup F}(\store) =
  \begin{cases}
    1 / |\stores| & \text{if}\ \store \in \stores\\
    0 & \text{otherwise}
  \end{cases}
  $$
  Then the \emph{program distribution of $\prog$}, denoted $\progd(\prog)$, is the
  marginal distribution of $S \cup V$ in $\prog$'s basic distribution:
  $$
  \progd(\prog) =  \margd{\pdf{S \cup V \cup F}}{S\cup V}
  $$
\end{definition}

>>>>

We consider random tapes to be selected from a uniform distribution.
In our threat model we will also assume that any possible initial
secrets are equally likely when formulating the program distribution.
In this setting, given a program $\prog$ with $\iov(\prog) = S \cup
V$ and $\flips(\prog) = F$ we will consider all $\store
\in \mems(S \cup V \cup F)$ such that
$
\config{\store_{S \cup F}}{\prog} \redxs \config{\store_}{\varnothing}
$
to be equally probable, establishing the basic distribution of the
program. From this we can immediately derive the marginal distribution
of $S \cup V$ to reason about dependencies between secrets and views. 
\begin{definition}
  \label{def-progd}
  Given progam $\prog$ with $\iov(\prog) = (S,V)$ and $\flips(\prog) = F$, define $\stores$ as:
  $$
  \stores \defeq \{ \store \mid (\dom(\store) = S \cup V \cup F) \wedge (\store_{S \cup F},\prog) \redxs (\store,\varnothing) \}
  $$
  Define also $\pdf{S \cup V \cup F}$ as the program's \emph{basic distribution} such that for all
  $\store \in \mems(S \cup V \cup F)$:
  $$
  \pdf{S \cup V \cup F}(\store) =
  \begin{cases}
    1 / |\stores| & \text{if}\ \store \in \stores\\
    0 & \text{otherwise}
  \end{cases}
  $$
  Then the \emph{program distribution of $\prog$}, denoted $\progd(\prog)$, is the
  marginal distribution of $S \cup V$ in $\prog$'s basic distribution:
  $$
  \progd(\prog) =  \margd{\pdf{S \cup V \cup F}}{S\cup V}
  $$
  In some cases we will also be concerned with the (joint)
  probabilities of expression interpretation given a preceding program
  execution, and we write $\progd(\prog, \be)$ to denote the program
  distribution $\progd(\prog;\eassign{\itv}{\be})$ where $\itv$ is a
  special variable that is never used in programs.
\end{definition}
